Papers

### 2023-02-13 papers.qmd
fix link
update papers

## 2022
**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, submitted, 2022.

@@

M. A. Ausdemore, A. McCombs, D. Ries, A. Zhang, K. Shuler, K. Goode, **J. D. Tucker** and J. G. Huerta, “A Probabilistic Inverse Prediction Method for Predicting Plutonium Processing Conditions”, *Frontiers in Nuclear Engineering-Nuclear Materials*. accepted 2022.[PDF](Papers/PuBASS_Frontiers_2022.pdf)

@@

"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022, [Slides](Presentations/2022SMU_Nov_22.pdf)

>>>>

## 2023
**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)

@@

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, accepted, 2022.

## 2022
M. A. Ausdemore, A. McCombs, D. Ries, A. Zhang, K. Shuler, K. Goode, **J. D. Tucker** and J. G. Huerta, “A Probabilistic Inverse Prediction Method for Predicting Plutonium Processing Conditions”, *Frontiers in Nuclear Engineering-Nuclear Materials*. 10.3389/fnuen.2022.1083164, 2022.[PDF](Papers/PuBASS_Frontiers_2022.pdf)

@@

"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022, [Slides](Presentations/SMU_Nov_22.pdf)
